Notation proposal

### 2011-05-31 analysis.tex
added some more text
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@795 ccdd05d5-56c1-461a-bf98-85f6876523b4

In this section we describe an implementation of the method described in
section \ref{label{sec:method}} suitable for rapid gravitational-wave searches
for compact binary coalescence.  The previous method requires several
computations that can be done before the analysis is actually underway.  Thus
we divide the procedure into two stages 1) an offline planning stage and 2) an
online, low latency filtering stage.  The offline stage can be done before the
analysis is started an updated asychronously whereas the online stage must keep
up with the detector output and produce search results as rapidly as possible.
In the next two subsections we describe what these stages entail.

@@

The planning stage proceeds as follows.  First, the templates are chosen by
covering the space of mass parameters with a hexagonal grid
\cite{PhysRevD.76.102004} in order to satisfy the minimum match criterion.
Next, the templates are subdivided into groups of neighbors called
``sub-banks'' that are appropriately sized so that each bank can be efficiently
handled by a single machine.  (In this paper, we will only study a single
sub-bank.)  Using our understanding of the time-frequency evolution of the
templates, we choose time slice boundaries such that all of the templates
within this sub-bank are sub-critically sampled at progressively lower sample
rates.  Next, the templates within this sub-bank are realized as \textsc{fir}
filter coefficients.  For each time slice, the templates are downsampled to the
appropriate sample rate.  Finally, the \textsc{svd} is applied to each time
slice in order to produce a set of orthogonal \textsc{fir} filters and a
reconstruction matrix that maps them back to the original templates.  The
downsampled orthogonal \textsc{fir} filter coefficients, the reconstruction
matrix, and the time slice boundaries are all saved to disk.

>>>>

In this section we describe an implementation of the method described in
section \ref{label{sec:method}} suitable for rapid gravitational-wave searches
for compact binary coalescence.  The previous method requires several
computations that can be done before the analysis is actually underway.  Thus
we divide the procedure into two stages 1) an offline planning stage and 2) an
online, low latency filtering stage.  The offline stage can be done before the
analysis is started an updated asychronously, whereas the online stage must keep
up with the detector output and produce search results as rapidly as possible.
In the next two subsections we describe what these stages entail.

@@

The choice of filter waveforms and singular value decomposition can be done in
advance and will be valid as long as the detector noise spectrum remains
roughly constant.  New filter waveforms can be computed asynchronously using
updated spectrum estimates as they are available.

The planning stage begins with choosing templates that cover the space of mass
parameters with a hexagonal grid \cite{PhysRevD.76.102004} in order to satisfy
the minimum match criterion, which assures a user specified maximum loss in SNR
for signals that fall in-between the chosen templates.  Next, the templates are
subdivided into groups of neighbors called ``sub-banks'' that are appropriately
sized so that each bank can be efficiently handled by a single computer.
Dividing the mass space into smaller sub-banks also aids in the computational
cost of the singular value decomposition.  Using our understanding of the
time-frequency evolution of the templates, we choose time slice boundaries as
in \eqref{FIXME} such that all of the templates within a sub-bank are
sub-critically sampled at progressively lower sample rates.  Next, the
templates within the sub-bank are realized as \textsc{fir} filter coefficients.
For each time slice, the templates are downsampled to the appropriate sample
rate.  Finally, the \textsc{svd} is applied to each time slice in order to
produce a set of orthogonal \textsc{fir} filters and a reconstruction matrix
that maps them back to the original templates.  The downsampled orthogonal
\textsc{fir} filter coefficients, the reconstruction matrix, and the time slice
boundaries are all saved to disk.
